\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-02 paper.tex
moved git stuff to appendix and working on heart section

% TODO this whole section should probably be in the appendix
\section{Version Control}
\label{sec:versionControl}

@@

\appendices
\section{Editour API Documentation}
\label{sec:editourAPIDocumentation}

@@

>>>>

@@

\appendices

% TODO should this really go in the appendix?
\section{Version Control}
\label{sec:versionControl}

\section{Editour API Documentation}
\label{sec:editourAPIDocumentation}

@@

\section{Ritsumeikan Heart Project}
\label{sec:ritsumeikanHeartProject}

\section{Supplies}
\label{sec:supplies}

\subsection{Project Goal}
\label{sec:projectGoal}

The goal of the project was to create an interactive model of a heart to teach
heart function to non-specialists, such as students in middle school. This meant
that the model had to be highly visual and simple to understand. Each visual
component would have to be designed in an intuitive fashion so that students
could begin interacting with the model without advanced knowledge of biology.

\subsection{The Heart Simulation}
\label{sec:theHeartSimulation}

We were presented with a set of equations that defined the mathematical model of
the heart we would be using to drive our physical model. Along with the
differential equations, we were also given an analogous circuit model that could
also be described by the same equations. The circuit and the equations can be
seen in Figure~\ref{fig:referenceModel}. We were also provided with source code
for an implementation of this model. We would still need to modify this code to
calculate the output variables we would need to properly operate the physical
model, and integrate the model into the main loop of the Arduino source code
with the appropriate timing.

\begin{figure}[h] \centering
    \includegraphics[width=0.4\textwidth]{reference-model.png}
    \caption{The reference model we used to implement the simulation}
    \label{fig:referenceModel}
\end{figure}

We visited ``Den Den Town'' in Osaka in order to gather supplies we would need
in order to construct the heart. One of the most important purchases of this
trip was a two-meter long strip of Adafruit NeoPixel light emitting diodes
(LEDs). The design of this reel of LEDs enabled us to cut the strip at specific
points to create shorter strips. Each LED on the strip individually adressable,
allowing us to set the color of any LED along the strip. This perfectly suited
our needs for representing blood flow.

We were able to program custom animations by updating the color and intensity of
the LEDs in a rapid fashion. We represented blood flow by changing the phase of
a sinusoidal wave over time.\footnote{For clarity, we elongated the ``troughs''
of the sine waves, so the pattern of intensity was not a true sine wave.} Our
design included two strips of twenty LEDs. The rate of the animation on the
first strip of LEDs represented blood flow out of the left ventricle.
